NMRlipids IV: Other than PC headgroups

### 2017-02-16 Manuscript/manuscript.tex
Lot of updates

Experimental order parameters for different lipid headgroups are
collected in Fig. \ref{HGorderParameters}.
\begin{figure}[]
  \centering
  \includegraphics[width=9.0cm]{../Figs/HGorderparameters.eps}
  \caption{\label{HGorderParameters}
    Order parameters for headgroup and glycerol backbone with different headgroups
  }
\end{figure}

@@

Ion binding affinity in lipid bilayer containing PC lipids can be 
measured by using C-H bond order parameters for headgroup $\alpha$ and
$\beta$ carbons by using the electrometer concept. The decrease of these 
order parameters is linearly proportional to the amount of bound charge 
in bilayer \cite{??,catte16}. The electrometer concept can be used also
for bilayers containing PC lipids mixed with charged lipids \cite{macdonal87,roux90,??}.
This is demonstrated in Figs \ref{OrderParametersWithCaCl},
\ref{OrderParametersWithCaClBELOW1M} and \ref{OrderParameterCHANGESWithCaClBELOW1M}, where PC headgroup order parameters 
as a function of CaCl$_2$ concentration are shown from experiments with POPC and PS or PG.
\begin{figure}[]
  \centering
  \includegraphics[width=9.0cm]{../Figs/LIPIDSwithCaCl.eps}
  \caption{\label{OrderParametersWithCaCl}
    PC headgroup order parameters as a function of CaCl concentration from experiments containing charged lipids.
    Pure DPPC data from \cite{akutsu81}, pure POPC data from \cite{altenbach84}, 
    POPC:POPS mixture data from \cite{roux90} and POPC:POPG mixture data from \cite{macdonald87}.
  }
  \todo{Check the NaCl concentrations in the samples.}
\end{figure}
\begin{figure}[]
  \centering
  \includegraphics[width=9.0cm]{../Figs/LIPIDSwithCaClBELOW1M.eps}
  \caption{\label{OrderParametersWithCaClBELOW1M}
    Figure \ref{OrderParametersWithCaCl} zoomed to smaller concentrations.
  }
\end{figure}
\begin{figure}[]
  \centering
  \includegraphics[width=9.0cm]{../Figs/CHANGESwithCaClBELOW1M.eps}
  \caption{\label{OrderParameterCHANGESWithCaClBELOW1M}
    Changes in order parameters
  }
\end{figure}

>>>>

Absolute values of experimental order parameters for different lipid headgroups are
collected in Fig. \ref{HGorderParameters}. Signs are measured only for PC as far as I know,
thus only absolute values are used for now.
\begin{figure}[]
  \centering
  \includegraphics[width=9.0cm]{../Figs/HGorderparameters.eps}
  \caption{\label{HGorderParameters}
    Absolute values of order parameters for headgroup and glycerol backbone with different headgroups
    from experiments. POPC values are from \cite{ferreira13}, DOPS from \cite{browning80} contains 0.1M of NaCl,
    POPG from \cite{borle85} contains 10nM PIPES, DPPE from \cite{seelig76}, E.coliPE and E.coliPG are from \cite{gally81}.
  }
\end{figure}

@@

Ion binding affinity in lipid bilayer containing PC lipids can be 
measured by using C-H bond order parameters for headgroup $\alpha$ and
$\beta$ carbons by using the electrometer concept. The decrease of these 
order parameters is linearly proportional to the amount of bound charge 
in bilayer \cite{??,catte16}. The electrometer concept can be used also
for bilayers containing PC lipids mixed with charged lipids \cite{macdonald87,roux90,??}.
This is demonstrated in Figs \ref{OrderParametersWithCaCl},
\ref{OrderParametersWithCaClBELOW1M} and \ref{OrderParameterCHANGESWithCaClBELOW1M}, where PC headgroup order parameters 
as a function of CaCl$_2$ concentration are shown from experiments with POPC and PS or PG.
\begin{figure}[]
  \centering
  \includegraphics[width=9.0cm]{../Figs/LIPIDSwithCaCl.eps}
  \caption{\label{OrderParametersWithCaCl}
    PC headgroup order parameters as a function of CaCl concentration from experiments containing charged lipids.
    Pure DPPC data from \cite{akutsu81}, pure POPC data from \cite{altenbach84}, 
    POPC:POPS mixture data from \cite{roux90}, POPC:POPG mixture data with 0.1M NaCl from \cite{macdonald87}
    and POPC:POPG mixture data without NaCl from \cite{borle85}.
  }
  \todo{Check the NaCl concentrations in the samples.}
\end{figure}
\begin{figure}[]
  \centering
  \includegraphics[width=9.0cm]{../Figs/LIPIDSwithCaClBELOW1M.eps}
  \caption{\label{OrderParametersWithCaClBELOW1M}
    Figure \ref{OrderParametersWithCaCl} zoomed to smaller concentrations.
  }
\end{figure}
\begin{figure}[]
  \centering
  \includegraphics[width=9.0cm]{../Figs/CHANGESwithCaCl.eps}
  \caption{\label{OrderParameterCHANGESWithCaClBELOW1M}
    Changes in order parameters
  }
\end{figure}
